\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-04-19 archive.tex
rough draft

We trained our system on 128 automatically-generated text editing tasks, with 4 input/output examples each.
We tested, but did not train, on the 108 text editing problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems within 10 minutes with an average search time of 235 seconds.
After learning,
it solves 79.6\%, and does so much faster,
solving them in an average of 40 seconds.
As of the 2017 SyGuS competition,
the best-performing synthesizer (CVC4) solves 82.4\% of the problems ---
but here, the competition conditions are 1 hour \& 8 CPUs per problem,
and with this more generous compute budget we
surpass
this previous
result and solve
84.3\% of the problems.
SyGuS additionally comes with a
different hand-engineered DSL \emph{for each text editing problem}. %\footnote{SyGuS text editing problems also prespecify the set of allowed string constants for each task. For these experiments, our system did not use this assistance.}
Here  we learned a single DSL
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

@@

\subsubsection{Programs for Smooth Trajectories}\label{regressionSection}
Many procedures that people learn, like as motor routines, can be
thought of as some kind of smooth trajectory. Modeling these
procedures as programs entails jointly inferring their combinatorial
structure and their continuous parameters.  We consider simple
programs generating trajectories described by polynomials (up to
degree 4) and rational functions, and equip our learner with a
primitive for introducing a continuous parameter into the discrete
structure of its programs, which an inner loop optimizes via gradient
descent. We penalize the use of real-valued parameters using a
BIC~\cite{Bishop:2006:PRM:1162264} likelihood model.  We use a convolutional neural
network as a `visual' recognition model, which observes a graph of the
trajectory over time, allowing the agent to `eyeball' the trajectory
prior to writing code that describes it
(Figure~\ref{symbolicRegressionExamples}).  In solving 100 such tasks,
the model learns to find programs minimizing the number of continuous
parameters --- this phenomenon arises from our Bayesian framing: both
the generative model's bias toward shorter programs, and the likelihood
model's BIC penalty.
\begin{figure}
    \includegraphics[width = \textwidth]{figures/sr16_horizontal.png}
  \caption{Sixteen smooth-trajectory tasks. Agent writes a program containing continuous real numbers that fits the points along the curve. Recognition model is a CNN that takes as input a graph of the trajectory over time (shown above). Task is `solved' if program matches points on curve.}\label{symbolicRegressionExamples}
  \end{figure}
\subsubsection{Programs that generate images}\label{logoSection}

@@

Inside its learned library we find interpretable parametric drawing
routines corresponding to the families of visual objects in its
training data, like polygons, circles, and spirals
(Figure~\ref{logoPrimitives}, middle) -- without supervision the agent
has learned the basic types of objects in its visual world. It
additionally learns more abstract visual relationships, like
rotational symmetry, which it models by abstracting out a new higher-order
function into its library.

@@

Inspired by the classic AI `copy task' --- where an agent must look at
an image of a tower made of toy blocks and re-create the
tower~\cite{towerCopy} --- we give \system 112 tower `copy tasks'
(Figure~\ref{tower}, top).  Here the agent observes both an image of a
tower and the locations of each of its blocks, and must write a
program that plans how a simulated hand would build the tower.
These towers are built from Lego-style blocks
that snap together on a discrete grid.
The system starts with the same control flow primitives as with
LOGO graphics,
and learns parametric `options' for building blocks towers (Figure~\ref{tower}, bottom left),
inferring concepts like arches, staircases, bridges and brick walls.
\begin{figure}
  \centering  \begin{tabular}{cc}
    \toprule
    \multicolumn{2}{c}{Subset of 112 Tasks}\\\midrule
    \multicolumn{2}{c}{\includegraphics[width = \textwidth]{figures/tower12.png}}\\\midrule \\
    \toprule Example learned DSL components&Samples written using final library\\\midrule
    \begin{tabular}{rl}
      Brickwall&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_bricks.png}
      \end{tabular}\\
      Bridge&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_bridge.png}
      \end{tabular}\\
      Staircase&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_staircase.png}
        \end{tabular}
    \end{tabular}&
    \begin{tabular}{l}
      \includegraphics[width = 6cm]{figures/tower/dreams.png}
      \end{tabular}
    \\\bottomrule 
    \end{tabular}
  \caption{\textbf{Top}: Twelve (out of 112) tower building tasks. Agent writes a program controlling a `hand' that builds the target tower. \textbf{Bottom left}: Three learned library routines. These components act like parametric options~\cite{stolle2002learning},
    giving higher-level building blocks that the agent can use to plan. \textbf{Bottom Right}: 16 random samples, or `dreams', built from learned library.}\label{tower}
\end{figure}

\subsubsection{Probabilistic Generative Modeling of Text}
Few-shot learning of simple generative concepts comes naturally to
humans, from learning new rules in natural language~\cite{marcus1999rule},
to learning routines for symbols and signs
\cite{lake2015human},
to learning new motor routines for producing words.
We investigate few-shot generative modeling by tasking our
agent with inferring a probabilistic regular expression from a small
number of strings, where these strings are drawn from CSV columns crawled from the web~\cite{LUKE}. Across wake/sleep cycles, our agent learns to learn
regular expressions that describe the structure of a typically occurring text concepts,
like numbers or dates.
Figure~\ref{qualitativeRegex} shows example model outputs on held out generative modeling tasks,
contrasting the full model with ablations that lesion either the library learning or recognition model training.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/regexQualitative.pdf}
  \caption{Qualitative results on probabilistic generative text modeling. Agent observes 5 strings (`Input' column) and infers a probabilistic regex (MAP program--regex primitives highlighted in red), from which it can imagine more examples of the latent text concept. No Library: Dreaming only (ablates library learning). No Rec: Consolidation only (ablates recognition model)}\label{qualitativeRegex}
\end{figure}

@@

We first task \system with inferring 57 equations describing physical laws,
like closed forms for ballistic motion, inverse square laws,
expressions for calculating centers of mass, etc.,
drawing verbatim from AP and MCAT physics `cheat sheets'
along with equation guides from machine learning textbooks.
These relationships are easy to express
given concepts like vectors or forces.
Rather than `bake in' abstractions like these we
initialize the system with Lisp-style sequence manipulation primitives like
\code{map} and \code{fold}.
We automatically convert each task into a
regression problem by randomly generating real or vector valued input/outputs,
and encode vectors as lists of reals.

@@

Could we also learn the basics of programming, including these recursive sequence manipulation primitives?
This goal is relevant to a long-standing dream within the program induction community to ``learn from scratch'': starting with a \emph{minimal} Turing-complete programming language,
and then learning to solve a wide swath of
induction problems~\cite{solomonoff1964formal,schmidhuber2004optimal,hutter2004universal,solomonoff1989system}.
All existing systems,
including ours,
fall far short of this dream,
and it is unclear (and we believe unlikely)
that this dream could ever be fully realized.
How far can we push in this direction?
``Learning from scratch'' is subjective, but a reasonable
starting point is the set of primitives provided in 1959
Lisp~\cite{mccarthy1960recursive}: these include
conditionals, recursion, arithmetic, and the 
list operators \code{cons}, \code{car}, \code{cdr}, and \code{nil}.
A  basic first goal is to start with
these primitives,
and then recover a DSL that
more closely resembles modern functional languages like Haskell and OCaml.

We ran the following experiment: \system was given a subset of the
1959 Lisp primitives, and tasked with solving 18 programming
exercises. A key difference between this setup and our previous
experiments is that, for this experiment, the system is given
primitive recursion, whereas previously we had sequestered recursion
within higher-order functions like \code{map}, \code{fold}, and
\code{unfold}.  In solving these 18 exercises, the algorithm assembles
a DSL containing a modern repertoire of functional programming idioms
and subroutines, including \code{map}, \code{fold}, \code{unfold},
\code{index}, \code{length}, and arithmetic operations like building
lists of natural numbers between an interval (see
Figure~\ref{librariesToLanguages}, right).

@@

    \begin{tabular}{c}
      \includegraphics[width = 5cm]{figures/learningCurves/regex_marginal_test_unigram_gen.png}\\
      \includegraphics[width = 5cm]{figures/learningCurves/regex_task_train_unigram_gen.png}
      \end{tabular}
  \end{tabular}
  \caption{Test set performance across wake/sleep iterations. Each curve is a run with a different random seed. Teal: Full model. Orange: Dreaming only (no DSL learning). Purple: Consolidation only (no recognition model). Search time plots show solid lines (time averaged over all tasks) and dotted lines (time averaged over solved tasks). Generative text modeling plots show (top) posterior predictive likelihood of held-out strings on held out tasks and (bottom) lower bound on marginal likelihood of held out tasks, both of which are averaged per character.}\label{learningCurves}      
\end{figure}

@@

\emph{(related work)} \system builds on several generations of research in AI, program synthesis,
and cognitive science, with program induction being one of the oldest
theoretical frameworks for concept learning within artificial
intelligence~\cite{solomonoff1964formal}, and the conceptually allied
`Language of Thought Hypothesis' being almost as
old~\cite{fodor1975language}. Recent neural program synthesis systems
pair a fixed domain-specific programming language (a `DSL') to a
learned neural network that guides program
search~\cite{spiral,balog2016deepcoder,devlin2017neural}, while recent
symbolic AI research has developed frameworks for learning the DSL by
inferring reusable pieces of
code~\cite{ecc,Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,DBLP:conf/ecai/LinDETM14}.
A main goal of this work is to combine and refine these techniques
with the intention of building agents that, like humans, develop
domain expertise for new classes of problems.  Work in cognitive
modeling has often exploited program-like representations for both
concept~\cite{piantadosi2011learning,lake2015human,GoodmanEtAl2015-Chapter} and intuitive theory
learning~\cite{logical,Ullman2012},
and we view these models of concept learning as
a kind of program induction,
and see theory learning as similar to inducing a DSL or library.

Our model alternatingly searches for solutions to tasks and then improves its search strategy;
within program induction, these principles were first elucidated by the Exploration-Compression (EC) algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.

Our work  sits within the Exploration-Compression (EC) family of
algorithms.  EC~\cite{Dechter:2013:BLV:2540128.2540316} algorithms alternate between searching, or
`exploring', the space of programs, and then updating their search
procedure by compressing solutions found during exploration. \system
grew directly out of research on EC-style systems and both of our
sleep phases can be interpreted as a kind of compression:
consolidation aims to compactly refactor code, while the recognition
model aims to encode a program in as few bits as possible, conditioned
on a task. %%  Our previous work, EC$^2$~\cite{ecc}, introduced
%% neurally-guided search into the EC framework and served as the
%% starting point for \systemEnding.  Our work here extends EC$^2$ by (1)
%% introducing a new refactoring compression algorithm, (2) enriching the
%% neural network with a new bigram-over-trees parameterization and loss
%% function that together learn to break symmetries, accelerating program
%% search during waking, and (3) demonstrating how this family of
%% approaches can be applied to planning and generative modeling
%% problems. 
Other offshoots of EC include our prior work, EC$^2$~\cite{ecc}, the neurosymbolic framework
in~\cite{lazaro2019beyond} and the hierarchical Bayesian program
learner in~\cite{DBLP:conf/icml/LiangJK10}. Closely aligned ideas go
even further back~\cite{solomonoff1989system,schmidhuber2004optimal}.

@@

Programs, as a knowledge representation,
hold promise because of their universal expressiveness and
compositional systemacity.
We are optimistic that programs can become a more standard part of the AI toolkit,
and that a key enabling insight will be combination of
explicit declarative concepts and implicit procedural skill, both jointly learned.

>>>>

We trained our system on 128 automatically-generated text editing tasks, with 4 input/output examples each.
We tested, but did not train, on the 108 text editing problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems within 10 minutes with an average search time of 235 seconds.
After learning,
it solves 79.6\%, and does so much faster,
solving them in an average of 40 seconds.
As of the 2017 SyGuS competition,
the best-performing synthesizer (CVC4) solves 82.4\% of the problems ---
but here, the competition conditions are 1 hour \& 8 CPUs per problem,
and with this more generous compute budget we
surpass
this previous
result and solve
84.3\% of the problems.
SyGuS additionally comes with a
different hand-engineered libraries of primitives \emph{for each text editing problem}. %\footnote{SyGuS text editing problems also prespecify the set of allowed string constants for each task. For these experiments, our system did not use this assistance.}
Here  we learned a single library of text-editing concepts
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

@@

\subsubsection{Programs for Smooth Trajectories}\label{regressionSection}
Many procedures that people learn, like as motor routines, can be
thought of as some kind of smooth trajectory. Modeling these
procedures as programs entails jointly inferring their combinatorial
structure and their continuous parameters.  We consider simple
programs generating trajectories described by polynomials (up to
degree 4) and rational functions, and equip our learner with a
primitive for introducing a continuous parameter into the discrete
structure of its programs, which an inner loop optimizes via gradient
descent. We penalize the use of real-valued parameters using a
BIC~\cite{Bishop:2006:PRM:1162264} likelihood model.  We use a convolutional neural
network as a `visual' recognition model, which observes a graph of the
trajectory over time, allowing the agent to `eyeball' the trajectory
prior to writing code that describes it
(Figure~\ref{symbolicRegressionExamples}).  In solving 100 such tasks,
the model learns to find programs minimizing the number of continuous
parameters --- this phenomenon arises from our Bayesian framing: both
the generative model's bias toward shorter programs, and the likelihood
model's BIC penalty.
\begin{figure}[b]
    \includegraphics[width = \textwidth]{figures/sr16_horizontal.png}
  \caption{Sixteen smooth-trajectory tasks. Agent writes a program containing continuous real numbers that fits the points along the curve. Recognition model is a CNN that takes as input a graph of the trajectory over time (shown above). Task is `solved' if program matches points on curve.}\label{symbolicRegressionExamples}
  \end{figure}
\subsubsection{Programs that generate images}\label{logoSection}

@@

Inside its learned library we find interpretable parametric drawing
routines corresponding to the families of visual objects in its
training data, like polygons, circles, and spirals
(Figure~\ref{logoMaster}, middle) -- without supervision the agent
has learned the basic types of objects in its visual world. It
additionally learns more abstract visual relationships, like
rotational symmetry, which it models by abstracting out a new higher-order
function into its library.

@@

Inspired by the classic AI `copy task' --- where an agent must look at
an image of a tower made of toy blocks and re-create the
tower~\cite{towerCopy} --- we give \system 112 tower `copy tasks'
(Figure~\ref{tower}, top).  Here the agent observes both an image of a
tower and the locations of each of its blocks, and must write a
program that plans how a simulated hand would build the tower.
These towers are built from Lego-style blocks
that snap together on a discrete grid.
The system starts with the same control flow primitives as with
LOGO graphics,
and inside its learned library we find parametric `options' for building blocks towers (Figure~\ref{tower}, bottom left),
including latent concepts like arches, staircases, bridges and brick walls.
\begin{figure}
  \centering  \begin{tabular}{cc}
    \toprule
    \multicolumn{2}{c}{Subset of 112 Tasks}\\\midrule
    \multicolumn{2}{c}{\includegraphics[width = \textwidth]{figures/tower12.png}}\\\midrule \\
    \toprule Example learned Library components&Samples written using final library\\\midrule
    \begin{tabular}{rl}
      Brickwall&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_bricks.png}
      \end{tabular}\\
      Bridge&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_bridge.png}
      \end{tabular}\\
      Staircase&\begin{tabular}{l}
        \includegraphics[width = 6cm]{figures/tower/tower_dsl_staircase.png}
        \end{tabular}
    \end{tabular}&
    \begin{tabular}{l}
      \includegraphics[width = 6cm]{figures/tower/dreams.png}
      \end{tabular}
    \\\bottomrule 
    \end{tabular}
  \caption{\textbf{Top}: Twelve (out of 112) tower building tasks. Agent writes a program controlling a `hand' that builds the target tower. \textbf{Bottom left}: Three learned library routines. These components act like parametric options~\cite{stolle2002learning},
    giving higher-level building blocks that the agent can use to plan. \textbf{Bottom Right}: 16 random samples, or `dreams', built from learned library.}\label{tower}
\end{figure}

\subsubsection{Probabilistic Generative Modeling of Text}
Few-shot learning of simple generative concepts comes naturally to
humans, from learning new rules in natural language~\cite{marcus1999rule},
to learning routines for symbols and signs
\cite{lake2015human},
to learning new motor routines for producing words.
We investigate few-shot generative modeling by tasking our
agent with inferring a probabilistic regular expression from a small
number of strings, where these strings are drawn from CSV columns crawled from the web~\cite{mws}. Across wake/sleep cycles, our agent learns to learn
regular expressions that describe the structure of a typically occurring text concepts,
like numbers or dates.
Figure~\ref{qualitativeRegex} shows example model outputs on held out generative modeling tasks,
contrasting the full model with ablations that lesion either the library learning or recognition model training.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/regexQualitative.pdf}
  \caption{Qualitative results on probabilistic generative text modeling. Agent observes 5 strings (`Input' column) and infers a probabilistic regex (MAP program--regex primitives highlighted in red), from which it can imagine more examples of the latent text concept. No Library: Dreaming only (ablates library learning). No Rec: Consolidation only (ablates recognition model)}\label{qualitativeRegex}
\end{figure}

@@

We first task \system with inferring 60 equations describing physical laws,
like closed forms for ballistic motion, inverse square laws,
expressions for calculating centers of mass, etc.,
drawing verbatim from AP and MCAT physics `cheat sheets'
along with equation guides from machine learning textbooks.
These relationships are easy to express
given concepts like vectors or forces.
Rather than `bake in' abstractions like these we
initialize the system with Lisp-style sequence manipulation primitives like
\code{map} and \code{fold}.
We automatically convert each task into a
regression problem by randomly generating real or vector valued input/outputs,
and encode vectors as lists of reals.

@@

Could we also learn the basics of programming, including these recursive sequence manipulation primitives?
This goal is relevant to a long-standing dream within the program induction community to ``learn from scratch'': starting with a \emph{minimal} Turing-complete programming language,
and then learning to solve a wide swath of
induction problems~\cite{solomonoff1964formal,schmidhuber2004optimal,hutter2004universal,solomonoff1989system}.
All existing systems,
including ours,
fall far short of this dream,
and it is unclear (and we believe unlikely)
that this dream could ever be fully realized.
How far can we push in this direction?
``Learning from scratch'' is subjective, but a reasonable
starting point is the set of primitives provided in 1959
Lisp~\cite{mccarthy1960recursive}: these include
conditionals, recursion, arithmetic, and the 
list operators \code{cons}, \code{car}, \code{cdr}, and \code{nil}.
A  basic first goal is to start with
these primitives,
and then recover a representation that
more closely resembles modern functional languages like Haskell and OCaml.

We ran the following experiment: \system was given a subset of the
1959 Lisp primitives, and tasked with solving 18 programming
exercises. A key difference between this setup and our previous
experiments is that, for this experiment, the system is given
primitive recursion, whereas previously we had sequestered recursion
within higher-order functions like \code{map}, \code{fold}, and
\code{unfold}.  In solving these 18 exercises, the algorithm assembles
a library containing a modern repertoire of functional programming idioms
and subroutines, including \code{map}, \code{fold}, \code{unfold},
\code{index}, \code{length}, and arithmetic operations like building
lists of natural numbers between an interval (see
Figure~\ref{librariesToLanguages}, right).

@@

    \begin{tabular}{c}
      \includegraphics[width = 5cm]{figures/learningCurves/regex_marginal_test_unigram_gen.png}\\
      \includegraphics[width = 5cm]{figures/learningCurves/regex_task_train_unigram_gen.png}
      \end{tabular}
  \end{tabular}
  \caption{Test set performance across wake/sleep iterations. Each curve is a run with a different random seed. Teal: Full model. Orange: Dreaming only (no library learning). Purple: Consolidation only (no recognition model). Search time plots show solid lines (time averaged over all tasks) and dotted lines (time averaged over solved tasks). Generative text modeling plots show (top) posterior predictive likelihood of held-out strings on held out tasks and (bottom) lower bound on marginal likelihood of held out tasks, both of which are averaged per character.}\label{learningCurves}      
\end{figure}

@@

\emph{(related work)} \system builds on several generations of research in AI, program synthesis,
and cognitive science, with program induction being one of the oldest
theoretical frameworks for concept learning within artificial
intelligence~\cite{solomonoff1964formal}, and the conceptually allied
`Language of Thought Hypothesis' being almost as
old~\cite{fodor1975language}. Recent neural program synthesis systems
pair a fixed domain-specific programming language (a `DSL') to a
learned neural network that guides program
search~\cite{DBLP:journals/corr/abs-1804-01118,balog2016deepcoder,devlin2017neural}, while recent
symbolic AI research has developed frameworks for learning the DSL by
inferring reusable pieces of
code~\cite{ecc,Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,DBLP:conf/ecai/LinDETM14}.
A main goal of this work is to combine and refine these techniques
with the intention of building agents that, like humans, develop
domain expertise for new classes of problems.  Work in cognitive
modeling has often exploited program-like representations for both
concept~\cite{piantadosi2011learning,lake2015human,GoodmanEtAl2015-Chapter} and intuitive theory
learning~\cite{logical,Ullman2012},
and we view these models of concept learning as
a kind of program induction,
and see theory learning as similar to inducing a DSL or library.

Our model draws on ideas first elucidated by the
Exploration-Compression family of algorithms~\cite{Dechter:2013:BLV:2540128.2540316,ecc,lazaro2019beyond,DBLP:conf/icml/LiangJK10,solomonoff1989system,schmidhuber2004optimal,ozkural2011teraflop},
which alternate
between searching, or `exploring', a space of solutions, and then
updating their search procedure by compressing solutions found during
exploration.  Both of our sleep phases can be interpreted as a kind of
compression: abstraction aims to compactly refactor code, while the
recognition model aims to encode a program in as few bits as possible,
conditioned on a task. What \system contributes here is the joint capture of
declarative aspects of domain knowledge -- considered in prior EC works -- and
the equally crucial procedural knowledge,
both of which human experts seem to need.

%% Our model alternatingly searches for solutions to tasks and then improves its search strategy;
%% within program induction, these principles were first elucidated by the Exploration-Compression (EC) algorithm~\cite{Dechter:2013:BLV:2540128.2540316}.

%% Our work  sits within the Exploration-Compression (EC) family of
%% algorithms.%%  Our previous work, EC$^2$~\cite{ecc}, introduced
%% %% neurally-guided search into the EC framework and served as the
%% %% starting point for \systemEnding.  Our work here extends EC$^2$ by (1)
%% %% introducing a new refactoring compression algorithm, (2) enriching the
%% %% neural network with a new bigram-over-trees parameterization and loss
%% %% function that together learn to break symmetries, accelerating program
%% %% search during waking, and (3) demonstrating how this family of
%% %% approaches can be applied to planning and generative modeling
%% %% problems. 
%% Other offshoots of EC include our prior work, EC$^2$~\cite{ecc}, the neurosymbolic framework
%% in~\cite{lazaro2019beyond} and the hierarchical Bayesian program
%% learner in~\cite{DBLP:conf/icml/LiangJK10}. Closely aligned ideas go
%% even further back~\cite{solomonoff1989system,schmidhuber2004optimal}.

@@

Programs, as a knowledge representation,
hold promise because of their universal expressiveness and
compositional systemacity.
We are optimistic that programs can become a more standard part of the AI toolkit,
and that a key enabling insight will be combination of
explicit declarative concepts and implicit procedural skill, both jointly learned.
Looking forward we anticipate that making machines which can \emph{simultaneously}
develop expertise for many different classes of problems, as humans do,
could be enabled by metalearning a library, DSL, or `language-of-thought':
learning a single generic programmatic substrate,
which can then differentiate itself into domain-specific
representations for many different classes of problems.
